A graph-based data model for interactive evolutionary computation

### 2017-01-17 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Starting model

% Begins Christian´s writings
% Needs TLC

@@

Users are a central part of this proposed framework as it aims to study their
behavior when interacting with individuals within interactive evolutionary
algorithms and other tasks that may exist within IEC systems. Thus users in
this proposal are entities interacting with an evolutionary computation that
has the fundamental purpose of evaluating individuals of a population
replacing the fitness function according to their preferences and mood, among
others []. This form of evaluate individual is given a subjectively way.

On the other hand in order to capture the attention of users and possibly
increase their participation, currently there exist some basic actions that
users can perform in a given system, going from to be able to access a system
through login mechanism, once the user has logged-in in to the system the
users can interact with different actions, for example the inviting action is
when users can be invited through social networks or maybe of person to
person. Another example is the sharing action, that can occur when users want
to share something of their interest through their social networks. In this sense the action of posting is when
users want to put something on their wall who want others to know through
their social networks. Likewise the storing action occurs when users want to
retain permanently information that are of their interest. Finally the
browsing action occurs when users are exploring content for their needs. All
these actions go beyond only evaluating individuals.

>>>>

Users are a central part of an IEC system, because not only their
explicit evaluation is involved, the overall context of interaction
affects the system as a whole as users interact not only with the graphical
interface, and each individual\'s phenotype, there is also the interaction
with other users, their previous evaluations and their own history of activities
and past experiences. Thus users in this proposal are dinamic entities 
interacting with an evolutionary computation and
have the fundamental purpose of evaluating individuals according to their preferences,
both explicitly or implicitly. Their degree of participation is affected by 
the context of use. With the porpouse of modeling the system, the contextual
factors are abstracted using a graph. This graph can then be used to 
enhance the system to capture the attention of users and possibly
increase their participation and mitigate the fatige.

The current model is tailored to the EvoSpace-I functionality and capabilities
but it can be modified to handle other platforms.

@@

Currently there exist some basic actions that
users can perform in the system, in order to interact with EvoSpace-I platform
users must login to the system through their facebook account. 
Once a user has logged-in to the system, he or she can do several actions.
Example of actions are the following:

\begin{enumerate}
  \item  Users can invite their friends to participate through social networks .

Another example is the sharing action, that can occur when In this sense the action of posting is when
users want to put something on their wall who want others to know through
their social networks. Likewise the storing action occurs when users want to
retain permanently information that are of their interest. Finally the
browsing action occurs when users are exploring content for their needs. All
these actions go beyond only evaluating individuals.
